intro

### 2022-03-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
updated documents
changed file location and added cross referencing

Every day we are confronted with stressful or emotionally demanding situations. 
The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] to regulate emotions is an important cognitive skill. 
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy [@Gross1998antecedent].
This postulated temporal sequence of ER strategies influences their effectiveness.
It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal [@Webb2012].
Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
Moreover, it is known that ER strategies reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG). [@Zaehringer2020]. 
<!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst. Corrugator habe ich raus genommen, weil auch Levator untersucht wird (müssten sonst m.E. beide genannt werden.) Generell fehlt noch etwas die Einbettung, warum die beiden ausgewählt wurden. Soll ich da noch etwas ergänzen? bei Zaehringer wird der Levator überhaupt nicht genannt, die Metaanalyse bezieht sich nur auf den Corrugator. Wir hatten damals gesagt, dass viele der negativen Bilder primär auch recht eklig sind und daher der Levator passender sein könnte, weil er speuzifisch auf Ekel zu reagieren scheint, der Corrugator hingegen auf negative Bilder im Allgemeinen. Prinzipiell haben wir aber für beide die gleichen Hypothesen. Können aber auch warten, was die Reviewer sagen.--> 
So these tactics from three different strategies proved to be effective in the short term. 
However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered. 
In particular, strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Longer lasting consequences of self-reported habitual use of ER strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the postulation of *adaptive* and *maladaptive* ER strategies.
For example, it was shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
In addition, a number of ER strategies have been associated with mental disorders (for meta-analytic review, see Aldao et al. [@Aldao2010]).

@@

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest *n*-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
Additionally, we will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).

```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can be represented by our paradigm.", out.width="98%"}
include_graphics(here("99_Thinktank","Other","Paradigm_Scheme_T2.png" ))
```

## 1.2 The present study

>>>>

Every day we are confronted with stressful or emotionally demanding situations. 
The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] to regulate emotions is an important cognitive skill. 
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy [@Gross1998antecedent].
This postulated temporal sequence of ER strategies influences their effectiveness.
It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal [@Webb2012].
Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
Moreover, it is known that ER strategies reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)[@Zaehringer2020] .
<!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst. Corrugator habe ich raus genommen, weil auch Levator untersucht wird (müssten sonst m.E. beide genannt werden.) Generell fehlt noch etwas die Einbettung, warum die beiden ausgewählt wurden. Soll ich da noch etwas ergänzen? bei Zaehringer wird der Levator überhaupt nicht genannt, die Metaanalyse bezieht sich nur auf den Corrugator. Wir hatten damals gesagt, dass viele der negativen Bilder primär auch recht eklig sind und daher der Levator passender sein könnte, weil er speuzifisch auf Ekel zu reagieren scheint, der Corrugator hingegen auf negative Bilder im Allgemeinen. Prinzipiell haben wir aber für beide die gleichen Hypothesen. Können aber auch warten, was die Reviewer sagen.--> 
So these tactics from three different strategies proved to be effective in the short term. 
However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered. 
In particular, strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Longer lasting consequences of self-reported habitual use of ER strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the postulation of *adaptive* and *maladaptive* ER strategies.
For example, it was shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
In addition, a number of ER strategies have been associated with mental disorders (for meta-analytic review, see Aldao et al. [@Aldao2010]).

@@

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest *n*-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
Additionally, we will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).

```{r ResponsePatterns, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can be represented by our paradigm."}
include_graphics(here("06_Paper", "ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
```
